Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-23 RR_manuscript/RR.Rmd
♻️ - edit per suggestion in #307

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.

>>>>

`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams with submissions meeting the criteria for inclusion in the meta-analytic model.
Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.
